### 2019-08-28 manuscript/manuscript.tex
new correction plot

Finally, we observed that in the longest run evolve-and-resequence study we
analyzed, some temporal covariances appeared to become negative at future
timepoints, a pattern that could be caused by advantageous fitness backgrounds
later becoming disadvantageous. The underlying causes could include
frequency-dependent selection, recombination disassociating beneficial and
deleterious alleles in repulsion linkage disequilibrium, or an environmental
change in the direction of selection. Thus far, our analysis has used
covariances averaged across the entire genome. Averaging over such large
numbers of loci is necessary to detect a signal of covariance in allele
frequency changes when both drift (inflated in evolve-and-sequence studies
which use small population sizes) and sampling variance can create spurious
covariances. However, the cost of using genome-wide covariances is that the
signal from regions harboring more additive genetic variance may be washed out
by noise. This is especially the case with detecting shifts in selection, which
are likely to be localized depending on the average effect of a region. To
address this limitation,

@@

>>>>

Finally, we observed that in the longest run evolve-and-resequence study we
analyzed \parencite{Barghi2019-qy}, some temporal covariances appeared to
become negative at future timepoints (see the first two rows in Figure
\ref{fig:figure-1} A). This could be caused by advantageous fitness backgrounds
later becoming disadvantageous, either due to frequency-dependent selection,
recombination breaking up a haplotype with coupled beneficial and deleterious
alleles, or or an environmental change in the direction of selection. However,
the signal of a change in the direction of selection may be washed out when we
calculate genome-wide temporal covariances. Averaging over such large numbers
of loci is necessary to detect a signal of covariance in allele frequency
changes when both drift (inflated in evolve-and-sequence studies which use
small population sizes) and sampling variance can create spurious covariances.
To address this limitation, we calculated temporal covariances over XXX Mb
windows, with on average XXX loci. While the covariance of each tile is noisy,
we can analyze the genome-wide distribution of tile covariances for changes
through time. We would like to compare the distribution of these tile
covariances to a neutral expectation, but a theoretically-determined neutral
null distribution would be inappropriate given complex dependencies across the
genome due to LD (which can occur over long physical distances in E&R and
selection studies, \cite{Nuzhdin2013-gf,Baldwin-Brown2014-cl}).

@@

\subsection{Correction}
\begin{figure}[!ht]
  \centering
  \includegraphics[]{figures/barghi-correction-plot.pdf}
  \caption{}
  \label{fig:figure-3}
\end{figure}
